Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-02-13 hpmoon-asoco.tex
More paragraphs divided

%1. MOP ARE
In MOPs, several
objectives have to be simultaneously optimized
\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies optimizing a function composed of several independent cost functions, one per objective. In
these problems the aim is to obtain a set of solutions that are better
than the rest considering all the objectives; this set is known as
the Pareto Front (PF). The solutions in this set are {\em non-dominated},
which means that there is no other solution that is equal or better
for all objectives; the objective of MOP algorithms is to find as many
solutions equally distributed in the Pareto Front as possible, and in order to do that the
exploration of the search space must be very efficient, trying to
cover many possible exploration paths at the same time.

%2 COMPUTATION -> PARALLEL
This aspect of searching for non-dominated solutions, as well as, in
many cases, the size of the search space itself, implies a high demand
of computational time, leading to the proposal of parallel and distributed methods to solve them
\citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268},
%3 ONE WAY IS TO USE MOEAS BECAUSE
one of which are evolutionary algorithms (EAs)
\citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
that can be effectively used to find nearly optimal solutions for
optimization problems and are easily parallelizable, since they are
population-based and creating a functionally equivalent parallel
version is as easy as distributing the population in communicating
computing nodes, which are usually called islands. The fact that
they are population-based helps find many solutions that compose the
Pareto front simultaneously.

@@

The number of generations between migrations has been set to 5,
as
reported by \cite{Deb03distributed,Martens13asynchronous}. In general
and as affirmed by 
\cite{cantu1998survey}, this migration gap has contradictory effects
on the result: by increasing it, we make the system closer to a
single-node one, since populations tend to mix without restriction; by
decreasing it, we make the isolate islands more prone to being stuck
in local minima. \cite{Martens13asynchronous} mentions that several
values were tested with no influence in the result; in our particular
case, the mixing is essential for the algorithm to spread the result
to all parts of the chromosome, so while we tend to agree with
M{\"a}rtens on the small influence of this value on the result, we also
think that making this value much bigger in our case would have a
negative impact. However, a precise fine-tuning of this value is left
as future work, as the main focus of this paper was to \textcolor{blue}{show} the
general concept, and not tune the values for maximum performance.

>>>>

%1. MOP ARE
In MOPs, several
objectives have to be simultaneously optimized
\citep{Mora13paretobased,LIU2017344}. Solving a MOP implies optimizing a function composed of several independent cost functions, one per objective. In
these problems the aim is to obtain a set of solutions that are better
than the rest considering all the objectives; this set is known as
the Pareto Front (PF). The solutions in this set are {\em non-dominated},
which means that there is no other solution that is equal or better
for all \textcolor{blue}{objectives. The} objective of MOP algorithms is to find as many
solutions equally distributed in the Pareto Front as \textcolor{blue}{possible. In} order to do that the
exploration of the search space must be very efficient, trying to
cover many possible exploration paths at the same time.

%2 COMPUTATION -> PARALLEL
This aspect of searching for non-dominated solutions, as well as, in
many cases, the size of the search space itself, implies a high demand
of computational time, leading to the proposal of parallel and distributed methods to solve them
\citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268},
%3 ONE WAY IS TO USE MOEAS BECAUSE
one of which are evolutionary algorithms (EAs)
\citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
that can be effectively used to find nearly optimal solutions for
optimization problems and are easily parallelizable, since they are
\textcolor{blue}{population-based. This means that} creating a functionally equivalent parallel
version is as easy as distributing the population in communicating
computing nodes, which are usually called islands. The fact that
they are population-based helps find many solutions that compose the
Pareto front simultaneously.

@@

The number of generations between migrations has been set to 5,
as
reported by \cite{Deb03distributed,Martens13asynchronous}. In general
and as affirmed by 
\cite{cantu1998survey}, this migration gap has contradictory effects
on the result: by increasing it, we make the system closer to a
single-node one, since populations tend to mix without restriction; by
decreasing it, we make the isolate islands more prone to being stuck
in local minima. \cite{Martens13asynchronous} mentions that several
values were tested with no influence in the result; in our particular
case, the mixing is essential for the algorithm to spread the result
to all parts of the \textcolor{blue}{chromosome. So,} while we tend to agree with
M{\"a}rtens on the small influence of this value on the result, we also
think that making this value much bigger in our case would have a
negative impact. However, a precise fine-tuning of this value is left
as future work, as the main focus of this paper was to \textcolor{blue}{show} the
general concept, and not tune the values for maximum performance.
